Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-24 doc/main_jfm.tex
updated 2-vesicle subsection

\begin{figure}
\centering
\includegraphics[height=2in]{N116_shear_0.pdf}
\includegraphics[height=2in]{N116_shear_2500.pdf}\\
\includegraphics[height=2in]{N116_shear_5000.pdf}
\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
  }
    \label{figure9}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{Trajectories of two-vesicle in a shear flow. The moving paths of two centroids of two Janus-vesicles are plotted in blue and red. Both starting centroids of two Janus-vesicles are on the $x$-axis. 
For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).}
    \label{figure10}
\end{figure}

@@

Figure~\ref{figure9} demonstrates the simulation results of two Janus-vesicles in a shear flow where the testing shear rate is $\chi=0.005$ and the flow is given by $\dot x = \chi y$. In panel (a), the starting frame, two center-of-mass positions are placed 
on the same horizontal level, at $(-10,0)$ and $(10,0)$. Since we already have a pre-relaxed $58$-body in previous sections, we duplicate the state to have the initial configuration (shown in panel (a)) in this section. 
As expected, there is no pressure jump between the internal and external fluids from the beginning of the
simulation and this is shown in the background pressure plot. Panels (b)-(d) show the configurations when $t = \{500,1000,1500\}$ 
and we observe that the rotation continues as time goes. The streamlines are plotted in the background 
for all panels and we include the numerical results using continuum model in all insets. 
The comparisons give a qualitative agreement between two models.

An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be seen and tuned. In other words, the adhesive behavior will be absent when two vesicles are centered 
at a different level and are well separated in $y$-direction. 
Moreover, we provide trajectories of a longer run of the simulation results in Figure~\ref{figure10}. In all panels, the blue and red curves represent the moving paths of two Janus-vesicle centroids and they move
nearly a round when $t=4000$ as shown in panel (h).

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
  }
    \label{figure11}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{Trajectories of different setups in two-vesicle in an extensional flow and the moving paths of two centroids of two Janus-vesicles are plotted in blue and red. (i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii) 
  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure11} presents the numerical results from the case (iii) and a 
  consistent flow rate is $\chi = 0.005$ for all cases.}
    \label{figure12}
\end{figure}

@@

With a similar setup in the case of two Janus-vesicles in a shear flow, we use the same two pre-relaxed $58$-body Janus-vesicles to perform the simulations when the flow type is an extensional flow with flow rate $\chi=0.005$. This extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
Figure~\ref{figure11} shows one set of numerical results when the centroids of two bodies are placed at
$(-10,-0.1)$ and $(10,0.1)$. With this setup, we can make sure that two Janus-vesicles will separate along 
$y$-direction eventually from empirical tests. Panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.  Since two bilayers are close enough from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamlines. The short range repulsion plays an important role to avoid structure collisions and this result can be compared with some findings in continuum modeling simulations. The pressure plots in Figure~\ref{figure11} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.

Figure~\ref{figure12} provides simulation results when the center-of-mass positions are placed differently.
One can notice that when two centroids are placed on the same horizontal level, two Janus-vesicles reach
an equilibrium state without separation as shown in case (i). If only one centroid is placed above the $x$-axis, for instance, case (ii), two Janus-vesicle move together toward the upward. This is the consequence when the adhesive effect beats the flow strength. Case (iii) is same as the case shown in Figure~\ref{figure11}. Finally, case (iv) has a larger initial separation in $y$-direction and two Janus-vesicle moves much faster toward 
$\pm y$-directions.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{Trajectories of two-vesicle in a shear flow. The moving paths of two centroids of two Janus-vesicles are plotted in blue and red. Both starting centroids of two Janus-vesicles are on the $x$-axis. 
For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).}
    \label{figure9}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{N116_shear_0.pdf}
\includegraphics[height=2in]{N116_shear_2500.pdf}\\
\includegraphics[height=2in]{N116_shear_5000.pdf}
\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
  }
    \label{figure10}
\end{figure}

@@

Figure~\ref{figure9} demonstrates the simulation results of two Janus-vesicles in a shear flow where the testing shear rate is $\chi=0.005$ and the flow is given by $\dot x = \chi y$. 
In panel (a), the starting frame, two center-of-mass positions are placed 
on the same horizontal level, at $(-10,0)$ and $(10,0)$. Since we already have a pre-relaxed $58$-body in previous sections, we duplicate the state to have the initial configuration (shown in panel (a)) in this section. 
In all panels, the blue and red curves represent the moving paths of two Janus-vesicle centroids and they move nearly a round when $t=4000$ as shown in panel (h). 
We observe that the rotation continues as time goes and an interesting event occurs in the simulation that an adhesive effect can be seen and tuned. In other words, the adhesive behavior will be absent when two vesicles are centered at a different level and are well separated in $y$-direction.

The fluid pressure profiles of snapshots are given in Figure~\ref{figure10}.
As expected, there is no pressure jump between the internal and external fluids from the beginning of the
simulation and this is shown in the background pressure plot. 
Panels (b)-(d) show the configurations when $t = \{500,1000,1500\}$ and 
the streamlines are plotted in the background for all panels. We include the numerical results using 
a continuum model in all insets and these comparisons give a qualitative agreement between two models.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{Trajectories of different setups in two-vesicle in an extensional flow and the moving paths of two centroids of two Janus-vesicles are plotted in blue and red. (i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii) 
  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure12} presents the numerical results from the case (iii) and a 
  consistent flow rate is $\chi = 0.005$ for all cases.}
    \label{figure11}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
  }
    \label{figure12}
\end{figure}

@@

With a similar setup in the case of two Janus-vesicles in a shear flow, we use the same two pre-relaxed $58$-body Janus-vesicles to perform the simulations when the flow type is an extensional flow with flow rate $\chi=0.005$. This extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
Figure~\ref{figure11} provides simulation results when the center-of-mass positions are placed differently.
One can notice that when two centroids are placed on the same horizontal level, two Janus-vesicles reach
an equilibrium state without separation as shown in case (i). If only one centroid is placed above the $x$-axis, for instance, case (ii), two Janus-vesicle move together toward the upward. This is the consequence when the adhesive effect beats the flow strength. In case (iii), two centroids have a small bias in $y$-direction and they
start to move apart along $\pm y$-direction. Finally, case (iv) has a larger initial separation in $y$-direction and two Janus-vesicle moves much faster toward $\pm y$-directions.

Figure~\ref{figure12} shows numerical results when the centroids of two bodies are placed at
$(-10,-0.1)$ and $(10,0.1)$, that is, case (iii) of Figure~\ref{figure11}. With this setup, 
we can make sure that two Janus-vesicles will separate along $y$-direction eventually and we compare the results against a continuum model as shown in all insets. 
Panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.  Since two bilayers are close enough from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamlines. In fluid pressure profiles, the pressure is initially high between the gap formed by two 
Janus-vesicles and decreases during the separation. The short range repulsion plays an important role to avoid structure collisions and this result can be compared with some findings in continuum modeling simulations.
